Global Climate and Atmospheric Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and \Spitzer\ Phase Curve Observations

### 2018-02-08 ms.tex
edits

In addition to calculating the fit rms compared to the photon noise, we also tested for the presence of red noise based on whether the rms decreases as expected when the light curve in binned in time.  If the noise is white (uncorrelated in time), the residuals are expected to decrease by a factor of $\sqrt{N}$, where $N$ is the number of points in a bin. Figure\,\ref{fig:rms} shows the binned residuals compared to expectations for white noise. The \HST/WFC3 and \Spitzer\ Channel 2 light curves agree well with expectations, whereas \Spitzer\ Channel 1 shows higher noise than expected as bin size increases. This test confirms the presence of time-correlated noise in the Channel 1 light curve that can be seen by eye in the residuals in Figure\,\ref{fig:phasecurves}. Both \Spitzer\ channels use the same detector, but Channel 1 data are more susceptible to time-correlated noise because the the point spread function is further undersampled at shorter wavelengths, making intrapixel sensitivity variations more pronounced.

@@

\subsection{Climate}
We fit three different models to characterize the planet's climate: a two-temperature map, the physically-motivated kinematic model of \cite{zhang17}, and a spherical harmonic map. We also fit the thermal phase variation with a sinusoid, which can be inverted to map the climate \citep{cowan08, cowan17}.  All of the models provide reasonable fits to the data, with $\chi^2_\nu$ near unity, but they yield significantly different temperature maps. Table\,\ref{table:model_comparison} lists the minimum and maximum temperatures for the best fit models to the WFC3 broadband and two Spitzer phase curves. We also list the  information criterion (BIC) and Aikike information criterion (AIC) values for the fits \citep[a $\Delta$BIC value greater than 10 constitutes strong evidence against a given model;][]{kass95}.

%The best fit model is either a sinusoid or spherical harmonics, depending on which criterion is used for model selection. The BIC generally favors the simpler spherical harmonics model because it penalizes model complexity relatively more than the AIC \citep{kass95}. The sinusoid has four free parameters (amplitude, phase offset, and eclipse midpoint and depth), whereas the spherical harmonics model has four (for degree two).  The kinematic and two temperature models tend to perform significantly worse ($\Delta$BIC and $\Delta$AIC greater than 10).  As illustrated in Figure\,\ref{fig:model_comparison}, the kinematic model is larger than the observed planet-to-star flux on the nightside, whereas the two temperature model overpredicts the flux at quadrature and underpredicts the dayside.

We compared the planet's minimum and maximum temperature for the three climate maps by computing the temperatures over a $100\times100$ grid in latitude and longitude. The kinematic model has the hottest dayside temperature, and the two-temperature model has the smallest. The differences in peak temperature for the models we consider ranges from $630\,\mathrm{K}$ for \Spitzer\ Channel 1 to $1070\,\mathrm{K}$ for the broadband WFC3 light curve. The minimum nightside temperature is also model-dependent: for the WFC3 data, the two-temperature model predicts a nightside temperature of zero Kelvin, whereas the best fit kinematic model has a nightside temperature of $1980\,\mathrm{K}$.  These differences arise because the kinematic model allows a steep temperature gradient on the dayside, so the substellar point is much hotter than the terminator, whereas the two temperature map imposes a constant dayside temperature.  The spherical harmonics model has an intermediate temperature gradient and fits the data the best. However, this model may not be physically realistic: on the nightside, it produces much higher temperatures at the poles than at the equator, contrary to predictions from GCMs (which we discuss in \S\,\ref{sec:gcm}).

@@

We also compared the GCM output to temperature maps retrieved with \texttt{spiderman}. Figure\,\ref{fig:model_comparison} shows the 0.01 bar temperature map for the $\tau_\mathrm{drag4}$ GCM compared to the best fit models. At this pressure, the GCM has minimum and maximum temperatures of $580$ and $3520$ K. The temperature gradient from the dayside to the terminator is intermediate between the kinematic and spherical harmonics models. The GCM predicts a cooler nightside than all models except the two-temperature model. We note that the GCM does not provide a perfect fit to the data, whereas multiple \texttt{spiderman} maps fit quite well, with large differences in temperature between them (see Table \,\ref{table:model_comparison}). Determining which models (if any) accurately describe the climate will require higher precision phase curves and/or eclipse mapping \citep[e.g.][]{dewit12}.

>>>>

In addition to calculating the fit rms compared to the photon noise, we also tested for the presence of red noise based on whether the rms decreases as expected when the light curve in binned in time.  If the noise is white (uncorrelated in time), the residuals are expected to decrease by a factor of $\sqrt{N}$, where $N$ is the number of points in a bin. Figure\,\ref{fig:rms} shows the binned residuals compared to expectations for white noise. The \HST/WFC3 and \Spitzer\ Channel 2 light curves agree well with expectations, whereas \Spitzer\ Channel 1 shows higher noise than expected as bin size increases. This test confirms the presence of time-correlated noise in the Channel 1 light curve that can be seen by eye in the residuals in Figure\,\ref{fig:phasecurves}. Both \Spitzer\ channels use the same detector, but Channel 1 data are more susceptible to time-correlated noise because the the point spread function is more undersampled at shorter wavelengths, making intrapixel sensitivity variations more pronounced.

@@

\subsection{Climate}
We fit three different models to characterize the planet's climate: a two-temperature map, the physically-motivated kinematic model of \cite{zhang17}, and a spherical harmonic map. We also fit the thermal phase variation with a sinusoid, which can be inverted to map the climate \citep{cowan08, cowan17}.  All of the models provide reasonable fits to the data, with $\chi^2_\nu$ near unity, but they yield significantly different temperature maps. Table\,\ref{table:models} lists the best fit minimum and maximum temperatures, as well as the mean day- and nightside temperatures. We also list the  information criterion (BIC) values for the fits \citep[a $\Delta$BIC value greater than 10 constitutes strong evidence against a given model;][]{kass95}.

%As illustrated in Figure\,\ref{fig:model_comparison}, the kinematic model is larger than the observed planet-to-star flux on the nightside, whereas the two temperature model overpredicts the flux at quadrature and underpredicts the dayside.

The best fit model is generally the spherical harmonics map. It has a lower BIC value than all the other models for the broadband WFC3 and \Spitzer\,$3.6\,\mu$m phase curves. For the $4.5\,\mu$m phase curve, the two temperature map provides the best fit, but it only lowers the BIC value by 2 relative to the spherical harmonics map, which is not a statistically significant improvement \citep{kass95}. The spherical harmonics model yields a mean dayside temperature near 2700 K, whereas the nightside is closer to 1800 K.  The other models produce more extreme day-night temperature gradients.  These differences arise because the kinematic model allows a steep temperature gradient on the dayside, so the substellar point is much hotter than the terminator, whereas the two temperature map imposes a constant dayside temperature.  The intermediate temperature gradient in the spherical harmonics model fits the data the best. However, this model may not be physically realistic: on the nightside, it produces much higher temperatures at the poles than at the equator, contrary to predictions from GCMs (which we discuss in \S\,\ref{sec:gcm}).

%The kinematic model has the hottest dayside temperature, and the two-temperature model has the smallest. The differences in peak temperature for the models we consider ranges from $630\,\mathrm{K}$ for \Spitzer\ Channel 1 to $1070\,\mathrm{K}$ for the broadband WFC3 light curve. The minimum nightside temperature is also model-dependent: for the WFC3 data, the two-temperature model predicts a nightside temperature of zero Kelvin, whereas the best fit kinematic model has a nightside temperature of $1980\,\mathrm{K}$.

@@

We also compared the GCM output to temperature maps retrieved with \texttt{spiderman}. Figure\,\ref{fig:model_comparison} shows the 0.01 bar temperature map for the $\tau_\mathrm{drag4}$ GCM compared to the best fit models. At this pressure, the GCM has minimum and maximum temperatures of $580$ and $3520$ K. The temperature gradient from the dayside to the terminator is intermediate between the kinematic and spherical harmonics models. The GCM predicts a cooler nightside than all models except the two-temperature model. We note that the GCM does not provide a perfect fit to the data, whereas multiple \texttt{spiderman} maps fit quite well, with large differences in temperature between them (see Table \,\ref{table:models}). Determining which models (if any) accurately describe the climate will require higher precision phase curves and/or eclipse mapping \citep[e.g.][]{dewit12}.
